---
title: "Data Preprocessing: Regression"
output:
  md_document:
    variant: gfm
---

# Data Preprocessing

```{r}
# Load libraries
library(caret)
library(mltools)
library(data.table)
library(car)
library(dplyr)
library(stringr)
```

```{r}
# Read the data
df <- read.csv("./../data/regression_data/input/player_data.csv")
```

```{r}
# Get initial dimensions
dim(df)
```

```{r}
names(df)
```

Following data preprocessing operations needs to be performed on the data:

```{r}
## Remove unnecessary columns
remove.columns <- c("X", "Based", "Name")
df <- df[,!(names(df) %in% remove.columns)]

## Remove correlated columns
cor.columns <- c("Int.90", "Clear", "Svt", "Svp", "Svh", "Saves", "Pens.Saved.Ratio")
df <- df[, !(names(df) %in% cor.columns)]

## Split the transfer value
df[c("Lower.Transfer.Value", "Upper.Transfer.Value")] <- str_split_fixed(df$Transfer.Value ," - ", 2)

# Function to clean transfer value
clean.transfer.value <- function(x){
  if (grepl("€", x, fixed = TRUE)){
    x = sub("€","",as.character(x))
  }
  
  if (grepl("K", x, fixed = TRUE)){
    return (as.numeric(sub("K","",as.character(x))) * 1000)
  } else if (grepl("M", x, fixed = TRUE)){
    return (as.numeric(sub("M","",as.character(x))) * 1000000)
  } else{
    return (x)
  }
}

# Clean Upper limit of transfer value
df$Upper.Transfer.Value <- as.numeric(unlist(apply(df["Upper.Transfer.Value"], 1, clean.transfer.value)))
df$Upper.Transfer.Value[is.na(df$Upper.Transfer.Value)] <-0 
# Clean Lower limit of transfer value
df$Lower.Transfer.Value <- as.numeric(unlist(apply(df["Lower.Transfer.Value"], 1, clean.transfer.value)))
# Swap values if upper limit < lower limit
swap_index = rownames(df[df$Upper.Transfer.Value<df$Lower.Transfer.Value,]) # Find the indexes for which upper limit < lower limit
for (i in 1:length(swap_index)){
  # Iterate over indexes swapping values
  temp = df$Lower.Transfer.Value[i]
  df$Lower.Transfer.Value[i] = df$Upper.Transfer.Value[i]
  df$Upper.Transfer.Value[i] = temp
}
# Remove the original column
df <- df[, !(names(df) %in% c("Transfer.Value"))]

## Remove columns with near zero variance
nz.columns <- c("Pen.R", "Con.90", "xSv..", "Sv..", "Svh", "Svt", "Svp", "Pens.Saved.Ratio", "Saves", "Saves.xSv.")
df <- df[, !(names(df) %in% nz.columns)]
```

Write this preprocessed data to a file so that it can be used for comparing models.

```{r}
# Save the data with outliers
write.csv(df, "./../data/regression_data/intermediates/preprocessed_data.csv", row.names = FALSE)
```

## Outliers Analysis

Though individual features seems to have a lot of outliers, the reality may not be the same. The data should be viewed holistically with the effect of variables on each other.

```{r}
## Check for outliers

# Create a model
glm.model <- glm(CA~., data=df)

# Get the outliers
outliers <- outlierTest(glm.model)
exclusion <- names(outliers[[1]])
exclusion <- as.numeric(unlist(exclusion))

df[exclusion,]
```

The outlier detection algorithm has detected outliers which can be removed from the dataset.

```{r}
# Remove the outliers
for(i in 1: length(exclusion))
{
  df = df[-exclusion[i],]
}
```

```{r}
# Save this new data to a file
write.csv(df, "./../data/regression_data/intermediates/preprocessed_data_without_outliers.csv", row.names = FALSE)
```
