---
title: "Data Modelling: Regression"
output:
  md_document:
    variant: gfm
---

# Data Modelling

Since the data has been cleaned, it can now be used to create the models.

```{r}
library(caret)
```

Let the start modelling with the data from which outliers are removed.

```{r}
# Load the data
df <- read.csv("./../data/regression_data/intermediates/preprocessed_data_without_outliers.csv")
```

```{r}
# Get the dimensions of data
dim(df)
```

## Partition the data

To evaluate the model, there should be a set of which the model has not seen and for which the labels are known. Hence, it is necessary to split the data into training and testing set.

```{r}
# Partitioning the data
?write.csv
partition = createDataPartition(df$CA, p=0.8, list = FALSE)
train = df[partition,]
test = df[-partition,]
```

```{r}
names(train)
```

```{r}
# Save the training and testing data
write.csv(train, "./../data/regression_data/intermediates/train.csv", row.names = FALSE)
write.csv(test, "./../data/regression_data/intermediates/test.csv", row.names = FALSE)
```

## Regression Algorithms

Following are the classification algorithms that will be used to model the data:

1.  Linear Regression
2.  kNN
3.  Decision Tree
4.  Bagging
5.  Random Forest
6.  Gradient Boosting
