---
title: "Linear Regression"
output:
  md_document:
    variant: gfm
---

# Linear Regression

Since the data has been cleaned, it can now be used to create the models.

```{r}
# Load libraries
library(caret)
library(nnet)
library(MASS)

# Load helpers
source("./../helpers/helper.R")
```

## Import data

To evaluate the model, there should be a set of which the model has not seen and for which the labels are known. Hence, it is necessary to split the data into training and testing set.

```{r}
# Read training and testing data
train <- read.csv("./../data/regression_data/intermediates/train.csv")
test <- read.csv("./../data/regression_data/intermediates/test.csv")
```

```{r}
names(train)
```

## Model Training

The model is first trained on the training data and then evaluated on testing data.

```{r}
# Model training
linear.model <- lm(CA~., data=train)
```

```{r}
summary(linear.model)
```

```{r}
# Model training with new significant variable
new.train <- train[, c(6, 7, 14, 15, 23, 26, 28, 30)]
new.linear.model <- lm(CA~., data=new.train)
summary(new.linear.model)
```

## Model Validation

```{r}
# Predict the samples from test data using the model
result <- predict(linear.model, test)

# Print the RMSE and MAE
cat(paste("RMSE: ", RMSE(result, test$CA), "\n", "MSE: ", RMSE(result, test$CA)^2, "\n", "MAE: ", MAE(result, test$CA)))
```

```{r}
# Save the results
save.reg.result(RMSE(result, test$CA), MAE(result, test$CA), "Linear Regression")
```

## Prediction with Unknown Data

```{r}
# Load the data
unk <- read.csv("./../data/regression_data/intermediates/unknown_data.csv")
dim(unk)

# Predict using the built model
prediction <- predict(linear.model, unk)
prediction
```
