---
title: "Decision Tree Regression"
output:
  md_document:
    variant: gfm
---

# Decision Tree

Since the data has been cleaned, it can now be used to create the models.

```{r}
# Load libraries
library(caret)
library(rpart)
library(MASS)
```

## Import data

To evaluate the model, there should be a set of which the model has not seen and for which the labels are known. Hence, it is necessary to split the data into training and testing set.

```{r}
# Read training and testing data
train <- read.csv("./../data/regression_data/intermediates/train.csv")
test <- read.csv("./../data/regression_data/intermediates/test.csv")
```

## Model Training

The model is first trained on the training data and then evaluated on testing data.

```{r}
# Model training
dtree.model <- rpart(CA~., data=train)
```

```{r}
summary(dtree.model)
```

## Model Validation

```{r}
# Predict the samples from test data using the model
result <- predict(dtree.model, test)

# Print the RMSE and MAE
cat(paste("RMSE: ", RMSE(result, test$CA), "\n", "MAE: ", MAE(result, test$CA)))
```

```{r}
varImp(dtree.model)
```
