---
title: "Data Preprocessing: Classification"
output:
  md_document:
    variant: gfm
---

# Data Preprocessing

Before modelling data, let us utilize insights from our EDA notebook to clean up the data.

```{r}
# Load libraries
library(caret)
library(mltools)
library(data.table)
library(car)
library(dplyr)
```

```{r}
# Read the data
df <- read.csv("./../data/classification_data/input/corporate_credit_rating.csv")
```

Following data preprocessing operations needs to be performed on the data:

1.  Correct the data types of the columns. Two columns needs correction which are *CIK* and *SIC Code*.
2.  There were 3 credit rating agencies for which there is insufficient data. The data present with respect to these 3 agencies will be removed.
3.  Apart from *Net Margin*, all the other correlated columns will be removed.
4.  All irrelevant columns will be removed such as *SIC Code*, *CIK*, *Corporation Name*, *Ticker*, and *Rating Date.* These columns will not provide any information to the model even if they are encoded to numeric values.
5.  The target class for which sufficient data is not present will be removed.
6.  All the categorical variables remaining will be either one-hot encoded or label encoded. Following columns will be encoded:
    1.  One-hot encoding:

        1.  Sectors

        2.  Rating Agencies

    2.  Label encoding:

        1.  Rating

```{r}
## Preprocessing

# Correct the data types of columns
df$CIK <- as.factor(df$CIK)
df$SIC.Code <- as.factor(df$SIC.Code)

# Remove data of under-represented rating agencies
rating.agency.freq <- data.frame(table(df$Rating.Agency))
nreq.rating.agencies <- rating.agency.freq[order(rating.agency.freq$Freq, decreasing = TRUE),]
nreq.rating.agencies <- tail(nreq.rating.agencies, 3)
nreq.rating.agencies <- nreq.rating.agencies$Var1
df <- df[!df$Rating.Agency %in% nreq.rating.agencies,]

# Remove correlated columns
num.data <- df %>% dplyr::select(where(is.numeric))
cor_mat <- cor(num.data)
index <- findCorrelation(cor_mat, .75)
col.remove <- colnames(cor_mat)[index]
col.remove <- col.remove[-length(col.remove)]
df <- df[!names(df) %in% col.remove]

# Remove ID columns and other irrelevant columns
df <- df[!names(df) %in% c("SIC.Code", "CIK", "Ticker", "Corporation", "Rating.Date")]

# Remove under-represented target variable observations
ratings.count.df <- data.frame(table(df$Rating))
rtl.data <- ratings.count.df[ratings.count.df$Freq<10,]
df <- df[!df$Rating %in% rtl.data$Var1,]

# Encode categorical columns
# Encode Rating Agencies and Sectors
df$Rating.Agency <- as.factor(df$Rating.Agency)
df$Sector <- as.factor(df$Sector)
new.df <- one_hot(as.data.table(df), cols=c("Rating.Agency", "Sector"))

# Ecode Target Column
rating.order <- c("AAA", "AA+", "AA", "AA-", "A+", "A", "A-", "BBB+", "BBB", "BBB-", "BB+", "BB", "BB-", "B+", "B", "B-", "CCC+", "CCC", "CCC-", "CC", "C", "D")
new.df$Rating <- as.factor(new.df$Rating)
rating.factors <- factor(new.df$Rating, levels=rating.order)
rating.factors <- as.numeric(rating.factors)
new.df$Rating <- rating.factors
```

Write this preprocessed data to a file so that it can be used for comparing models.

```{r}
# Save the data with outliers
write.csv(new.df, "./../data/classification_data/intermediates/preprocessed_data.csv", row.names = TRUE)
```

## Outliers Analysis

Though individual features seems to have a lot of outliers, the reality may not be the same. The data should be viewed holistically with the effect of variables on each other.

```{r}
## Check for outliers

# Create a model
glm.model <- glm(Rating~., data=new.df)

# Get the outliers
outliers <- outlierTest(glm.model)
exclusion <- names(outliers[[1]])
exclusion <- as.numeric(unlist(exclusion))

new.df[exclusion,]
```

The outlier detection algorithm has detected 1 outlier which can be removed from the dataset.

```{r}
# Remove the outliers
for(i in 1: length(exclusion))
{
  new.df = new.df[-exclusion[i],]
}
```

```{r}
# Save this new data to a file
write.csv(new.df, "./../data/classification_data/intermediates/preprocessed_data_without_outliers.csv", row.names = TRUE)
```
